Placeholder

### 2021-02-22 Paper_Histograms.Rmd
Added extra subset for GLAD/EDGI pt's to use for all the prepan plots

```{r Merge GLAD/EDGI samples together for plot}

>>>>

```{r Create GLAD/EDGI prepan subset for prepan plots}

GLAD.prepan_with_EDGI <- dat.prepan %>% 
  filter(Sample == "GLAD" |
           Sample == "EDGI")

GLAD.prepan_with_EDGI %>% 
  group_by(Sample) %>% 
  summarise(N = n())

```{r Create NBR/EDGI labelled sample variable for retro plots}
